Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-09 paper/main.tex

\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}

Thorough problem description

@@

\chapter{Background technologies}
% Find new and better title

@@

\subsection{\ac{SUPERCOP}}
% TODO: Sjekk hvordan det er med sitering her
\ac{SUPERCOP} is a toolkit developed by VAMPIRE lab for measuring performance
of cryptographic software\cite{s_supercop}. In relation to hash functions
\ac{SUPERCOP} measures the following:

@@

The round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a
number of different optimalizations for each candidate. Optimalizations range
from 32-/64-bit optimalizations, the use of extended instruction sets such as
\ac{SSE2} and \ac{SSSE3}, optimalizations for different number of cores and
others. Also the toolkit will try different compiler-optimalizations to get the
best results possible for each function.
% Skal jeg sitere kildekode her?

@@

\chapter{Procedure}

TODO: We have to figure out a new title
Keywords: Python bindings in detail, unit tests, using it in Tahoe-LAFS

A bit more technical description of how we tested the candidates in Tahoe-LAFS

Limitations/assumptions

Error sources.

\chapter{Results}

What is tested and what is not tested?

tables, graphs?

\chapter{Discussion}

@@

\cite{s_nistround2}

\chapter{Conclusion}

A somewhat short conclusion summing up results and discussion

\section{Future work}

>>>>

%**************************************%
\chapter{Introduction}
%**************************************%
\pagenumbering{arabic}
\setcounter{page}{1}

Thorough problem description. \\
Stepwise, what will we actually do?

@@

%**************************************%
\chapter{Background technologies}
%**************************************%
% FIXME: Find new and better title

@@

\subsection{\ac{SUPERCOP}}
% TODO: Mention that some SUPERCOP candidates are missing UPDATE-functionality.
\ac{SUPERCOP} is a toolkit developed by VAMPIRE lab for measuring performance
of cryptographic software\cite{s_supercop}. In relation to hash functions
\ac{SUPERCOP} measures the following:

@@

The round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a
number of different optimalizations for each candidate. Optimalizations range
from 32-/64-bit optimalizations, the use of extended instruction sets such as
\ac{SSE2} and \ac{SSSE3}, optimalizations for different number of cores and
others. Also the toolkit will try different compiler-optimalizations to get the
best results possible for each function.
% Skal jeg sitere kildekode her?
% TODO: Insert image to visualize the forest of different implementations.

@@

%**************************************%
\chapter{Procedure}
%**************************************%

% FIXME: A more descriptive/better chapter title
%
%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.

In this chapter we will outline the procedure followed to complete our task.

\section{Choosing implementations of the SHA-3 Candidates}

% sphlib, SUPERCOP, NIST

\section{Python bindings}

Since Tahoe-\ac{LAFS} is written in Python, we needed some way of interacting
with the C implementations of the NIST candidates.

\subsection{Unit tests}
% Include the use of Known Answer Tests

\section{Modifications in the Tahoe-LAFS Code}

% This should be a short text, but maybe drag in a discussion of how we SHOULD
% have implemented it if we had the time, ref. capabilities.

\section{Test vectors and Configuration}

\subsection{Physical Setup}

\section{Distribution of the Code}
% Distutil, bash scripts

%**************************************%
\chapter{Measurements and Results}
%**************************************%

% Maybe cite
% \url{http://tahoe-lafs.org/trac/tahoe-lafs/wiki/Performance?version=32}
What is tested and what is not tested?

How much time is spent on hashing versus upload over network?

How much gain can Tahoe-LAFS get by switching to SHA-3?

Plenty of tables, graphs

%**************************************%
\chapter{Discussion}
%**************************************%

@@

%**************************************%
\chapter{Conclusion and Future Work}
%**************************************%

A somewhat short conclusion summing up what has been done, and results and
discussion
